### 2025-05-27 conteudo/apendices/survey.tex
add full answers of survey

\textbf{Answer 2:}

@@

\textbf{Answer 2:}

@@

\textbf{Answer 2:}

@@

@@

@@

@@

\textbf{Answer 2:}

>>>>

\textbf{Answer 2:} It was clear. The installation process was easy, just copy and paste. Score: 5 out of 5.

@@

\textbf{Answer 2:} The readme is direct and explains how to use the tool. An example would be nice,
something like a video or gi. It also would be good to have more detailed documentation
or hints for the use process. Score: 4 out of 5.

@@

\textbf{Answer 2:} I experienced a few errors. The first was related to disk space. I selected a path with a
lot of data, a huge code base, so it takes many minutes and disk space. In some cases,
the tool stops with some error but fortunately saves the process before stopping.
Score: 4 out of 5.

@@

\textbf{Anyyswer 2:} The results are clear and text colors help to understand them better. The final results are
displayed but not saved, it would be nice to also save them for future reference. Score: 4 out 5.

@@

\textbf{Anyyswer 2:} Yes, I detected many duplicates, it was fast and simple to use.

@@

\begin{itemize}

\item Multiple search, enables the possibility to have several tmp files and to select one
of them.

\item Different methods to find duplicates.

\item Define a threshold to the number of repeated lines, for example, find duplicates
with more than 90\% of similarity and more than 20 lines repeated.

\end{itemize}

@@

\textbf{Answer 2:} It was a great tool and a good experience.
